---
title: "MATH1324 Assignment 3"
subtitle: "Supermarket Price Wars"
output: html_notebook
---

## Group/Individual Details

* Alistair Grevis-James (s3644119)

## Executive Statement

In your own words, provide a brief summary of the investigation. Explain the aim of the investigation, the procedure, sample, variables, main findings and conclusions. Write this section last after you have performed hypothesis testing. (Word count Max: 300 words)

### Introduction & Hypothesis

Coles Supermarkets Australia Pty Ltd (trading as Coles) and Woolworths Supermarkets (colloquially known as "Woolies") were founded in Australia in 1914 and 1924, respectively ("Coles creates 115 jobs at its milestone 800th supermarket". www.wesfarmers.com.au. Retrieved 2017-07-02., Zappone, Chris (9 November 2009). "Supermarket duopoly blamed for soaring food prices". The Sydney Morning Herald. Retrieved 29 July 2013). Together, they make up more than 80% of the Australian market. Both Coles and Woolworths market themselves as extremely price competitive, whilst maintaining high quality products and a wide range (http://www.smh.com.au/business/retail/coles-deepens-price-war-after-slicing-bread-prices-20170712-gxa33p.html). Over the course of this investigation, we will attempt to determine price differences between Coles and Woolworths by evaluating two hypothesis.

### Hypothesis A
While Coles and Woolworths both claim to be "low cost", invariably, one supermarket chain will have lower prices.

### Hypothesis B
In an attempt to differentiate themselves from each other as 'low price' (while still maintaining high quality & a wide range), the two major Australian supermarket chains, Coles and Woolworths, will employ different pricing stratergies to show consumers they have the 'lowest prices'.

### Data Collection NOTE THE WAY FULL PRICE AND SALE WAS COLLECTED.
The price comparison website www.frugl.com.au was used for data collection. Data was collected over three days (7 Sep, 17 Sep & 18 Sep 2017) within the postcode 3054 (Carlton North, Victoria, Australia). Date was noted as sale items will change with time (and thus collection was performed within an 11 day window). Postcode was kept constant as different regions will presumably have specials and full priced products based on geographies (for example shops in QLD may sell mangos at much cheaper prices than in Victoria). Such assumption could be evaluated, however is outside the scope of this investigation.

Frugl allows filtering of products into a selection of distinct native categories, for example HEALTH & BEAUTY or BAKING. Categories were chosen based on the likelyhood of containing identical products. For example Nivea Moisturiser 200g is manufactured and thus identical, whereas Coles may stock Fresh Celery 250g while Woolworths may stock Farm Fresh Celery 225g. These subtle differences make comparison harder, and so products like the latter were ignored. The native categories and their respective item counts will be explored below.

Data was collated into a Google Sheet, which was pulled directly into the R Markdown environment. See below for data structure and importation methology.

## Load Packages and Data
```{r}
library(ggplot2)
library(dplyr)
library(gsheet)
library(vembedr)
library(gridExtra)
library("htmltools")
ds <- gsheet2tbl('https://drive.google.com/open?id=1_6RZ0HXg7VbgO78oyFfUyZaFOUHYWijy8XH1_jw5tA4')
###Note - "Overall Coles in cheaper, in category x coles in cheaper... and so on"
```

## Summary Statistics

### Data Checking and Initial Visualization
The importation of the data set from Google Sheets as 'ds' was checked with summary, and the attribute names were also checked using sapply. During data collection, identical items available at both Coles and Woolworths were chosen. These items came from the following native categories on the Frugl website - BAKING, DAIRY & EGGS DIETARY, HEALTH & LIFESTYLE, DRINKS, FROZEN FOOD, HEALTH & BEAUTY, PACKAGED & READY MEALS and PANTRY, value counts can be seen below. During data collection, these items were re-categorized into the following categories - Beauty, Diet/ Gym Food, Sugary Snack and Supplement, value counts can also be seen below. For this investigation the allocated categories will be used, as they contain the same number of products but spread over fewer groupings. In many cases the allocated categories more accuratly group the products, for example in the code block "#Exploring the Allocated Categories" we see four items that easy can be categorized together as sugary snacks.
```{r}
#Displaying summary statistics
summary(ds)
```
```{r}
#Checking the column names and corresponding data types
sapply(ds, typeof)
```
```{r}
#Value counts for the native categories
table(ds$`Native Category`)
```
```{r}
#Value counts for the allocated categories
table(ds$`Allocated Category`)
```
```{r}
#Exploring the Allocated Categories
df[c(281,286,291,300),c(2,3,4)]
```
The attributes "Unit" and "Amount" refer to the unit of measurement the product comes in and the amount, respectively (see exploration code blocks below). Value counts were used to check the categorical attribute Unit. A scatter plot was used explore amount.
```{r}
#Exploring Unit and Amount - Data Selection
df[c(9,47,17,234,283,409),c(2,4,9,10)]
```
```{r}
#Value Counts for Unit
table(df$`Unit`)
```
```{r}
#Exploring Unit and Amount - Dot Plot
qplot(data=ds, x=Amount, y=ds$`Allocated Category`, colour = ds$`Allocated Category`, main = 'Dot Plot of Allocated Category vs Amount',  ylab = 'Allocated Category', xlab = 'Amount (g, mL, pack)') + theme(legend.title=element_blank())
```
```{r}
#Exploring Unit and Amount - Stacked Histogram
qplot(data=ds, x=Amount, fill = ds$`Allocated Category`, colour = I("Black"), main = 'Stacked Histogram of Allocated Category vs Amount', xlab = 'Amount (g, mL, pack)') + theme(legend.title=element_blank())
```
The exploration up until this point has highlighted numerous challenges working with the data set. The products are distributed between three units, grams (g), milli litres (mL) & pack. Pack has a different meaning in the context of the products. For example (refer to the exploring unit and amount code block above) Tresemme Extra Hold Hair Spray (75g) has units g, with an amount of 75. John Frieda Medium Ash Blonde Hair Colour (1 pack) has the unit pack (not volume or mass) and a quantity of one. In the Supplement category Ostelin Vitamin D & Calcium Tablets (180 pack) has unit pack and quantity 180. The data will be explored further and standardised, as described below.

## Exploring the Native Continuous Data with Scatter Plots
Prior to any transformations, the data was also explored with scatterplots (see below).  
```{r}
qplot(data=ds, x=Coles, y=Woolworths, colour = ds$`Allocated Category`, main = 'Woolworths versus Coles Full Price Scatter Plot',  ylab = 'Woolworths Items (AUD)', xlab = 'Coles Items (AUD)') + theme(legend.title=element_blank())
```
```{r}
qplot(data=ds, x=ds$`Coles Sale`, y=ds$`Woolworths Sale`, colour = ds$`Allocated Category`, main = 'Woolworths Sale versus Coles Sale Scatter Plot',  ylab = 'Woolworths Sale Items (AUD)', xlab = 'Coles Sale Items (AUD)') + theme(legend.title=element_blank())
```
```{r}
qplot(data=ds, x=ds$`Woolworths Sale`, y=Woolworths, colour = ds$`Allocated Category`, main = 'Woolworths Sale Price versus Woolworths Full Price Scatter Plot',  ylab = 'Full Price Items (AUD)', xlab = 'Sale Items (AUD)') + theme(legend.title=element_blank())
```
```{r}
qplot(data=ds, x=ds$`Coles Sale`, y=Coles, colour = ds$`Allocated Category`, main = 'Coles Sale Price versus Coles Full Price Scatter Plot',  ylab = 'Full Price Items (AUD)', xlab = 'Sale Items (AUD)') + theme(legend.title=element_blank())
```




## Restructuring the Data
Four new data sets were created, one for each of the 
```{r}
#Exploring Unit and Amount - Data Selection

```

## Filtering for Specific Rows (Allocated Category = Beauty, Sugary Snack, Diet / Gym Food, Supplment)
Line 1 = Creating the filter
Line 2 = Creating the dataset (for Coles, Coles Sale, Woolworths, Woolworths Sale)
```{r}
beauty_filter <- ds$`Allocated Category` == "Beauty"
beauty_data <- ds[beauty_filter,]
sugarySnack_filter <- ds$`Allocated Category` == "Sugary Snack"
sugarySnack_data <- ds[sugarySnack_filter,]
dietGymFood_filter <- ds$`Allocated Category` == "Diet/ Gym Food"
dietGymFood_data <- ds[dietGymFood_filter,]
supplement_filter <- ds$`Allocated Category` == "Supplement"
supplement_data <- ds[supplement_filter,]
```




### Scatter Plot Visualization

```{r}

```









#Categories = analytics are more finely grained
#Standardize units = analytics are more finely grained


###We are now going to veiw native histograms for ALLOCATED CATEGORIES

### Initial Data Exploration




```{r}
#Coles (full price), for sugary snack
mean_coles_sugarySnack <- mean(ds$coles, select(ds$`Allocated Category` = 'Sugary Snack'))
ds$Coles == 'Sugary Snack'

summary(ds)
```



Walk through the data...

Use R to summarise the data from the investigation. 

Include an appropriate plot to help visualise the data. Describe the trend. 

```{r}
# This is a chunk for your summary statistics and visualisation code
ds$Coles
```

```{r}
#Creating new data set for allocated category sugary snack data
#Creating a filter
sugarySnack_filter <- ds$`Allocated Category` == "Sugary Snack"
#Creating the data set
sugarySnack_data <- ds[sugarySnack_filter,]
#In this instance we will take grams and mL to be equal (as at SLP, 1 mL has a mass of 1 g)

#Check units
table(sugarySnack_data$`Unit`)

sugarySnack_data$PriceMass <- 1000 / sugarySnack_data$Amount
sugarySnack_data$Per1000gPrice_Coles <- sugarySnack_data$PriceMass * sugarySnack_data$Coles
sugarySnack_data$Per1000gPrice_WW <- sugarySnack_data$PriceMass * sugarySnack_data$Woolworths
sugarySnack_data$Per1000gPrice_ColesSale <- sugarySnack_data$PriceMass * sugarySnack_data$'Coles Sale'
sugarySnack_data$Per1000gPrice_WWSale <- sugarySnack_data$PriceMass * sugarySnack_data$'Woolworths Sale'
#Stats - Native

mean_sugarySnack_coles <- mean(sugarySnack_data$Coles)
sd_sugarySnack_coles <- sd(sugarySnack_data$Coles)
hist(sugarySnack_data$Coles, xlim = c(0,20), ylim = c(0, 0.35), col="grey", xlab="Price AUD (variable amount g or mL)",main="Histogram of Sugary Snacks at Coles (full price)", breaks = 11, freq = FALSE)
curve(expr = dnorm(x, mean=mean_sugarySnack_coles, sd = sd_sugarySnack_coles), col="darkblue", lwd=2,   add=TRUE)

mean_sugarySnack_colesSale <- mean(sugarySnack_data$'Coles Sale')
sd_sugarySnack_colesSale <- sd(sugarySnack_data$'Coles Sale')
hist(sugarySnack_data$'Coles Sale', xlim = c(0,10), ylim = c(0, 0.5), col="grey", xlab="Price AUD (variable amount g or mL)", main="Histogram of Sugary Snacks at Coles (sale price)", freq = FALSE)
curve(expr = dnorm(x, mean=mean_sugarySnack_colesSale, sd = sd_sugarySnack_colesSale), col="darkblue", lwd=2, add=TRUE)

mean_Per1000gPrice_Coles <- mean(sugarySnack_data$Per1000gPrice_Coles)
sd_Per1000gPrice_Coles <- sd(sugarySnack_data$Per1000gPrice_Coles)
hist(sugarySnack_data$Per1000gPrice_Coles, xlim = c(-10,100), ylim = c(0, 0.04), col="grey", xlab="Price (per 1000 g or mL)", main="Histogram of Sugary Snacks at Coles (full price)", freq = FALSE)
curve(expr = dnorm(x, mean=mean_Per1000gPrice_Coles, sd = sd_Per1000gPrice_Coles), col="darkblue", lwd=2, add=TRUE)

mean_Per1000gPrice_ColesSale <- mean(sugarySnack_data$Per1000gPrice_ColesSale)
sd_Per1000gPrice_ColesSale <- sd(sugarySnack_data$Per1000gPrice_ColesSale)
hist(sugarySnack_data$Per1000gPrice_ColesSale, xlim = c(-10,100), ylim = c(0, 0.05), col="grey", xlab="Price (per 1000 g or mL)", main="Histogram of Sugary Snacks at Coles (sale price)", freq = FALSE)
curve(expr = dnorm(x, mean=mean_Per1000gPrice_ColesSale, sd = sd_Per1000gPrice_ColesSale), col="darkblue", lwd=2, add=TRUE)

mean_sugarySnack_Woolworths <- mean(sugarySnack_data$Woolworths)
sd_sugarySnack_Woolworths <- sd(sugarySnack_data$Woolworths)
hist(sugarySnack_data$Woolworths, xlim = c(0,20), ylim = c(0, 0.35), col="grey", xlab="Price AUD (variable amount g or mL)",main="Histogram of Sugary Snacks at WW (full price)", breaks = 11, freq = FALSE)
curve(expr = dnorm(x, mean=mean_sugarySnack_Woolworths, sd = sd_sugarySnack_Woolworths), col="darkblue", lwd=2,   add=TRUE)

mean_sugarySnack_WoolworthsSale <- mean(sugarySnack_data$'Woolworths Sale')
sd_sugarySnack_WoolworthsSale <- sd(sugarySnack_data$'Coles Sale')
hist(sugarySnack_data$'Coles Sale', xlim = c(0,10), ylim = c(0, 0.5), col="grey", xlab="Price AUD (variable amount g or mL)", main="Histogram of Sugary Snacks at Coles (sale price)", freq = FALSE)
curve(expr = dnorm(x, mean=mean_sugarySnack_colesSale, sd = sd_sugarySnack_colesSale), col="darkblue", lwd=2, add=TRUE)

mean_Per1000gPrice_Coles <- mean(sugarySnack_data$Per1000gPrice_Coles)
sd_Per1000gPrice_Coles <- sd(sugarySnack_data$Per1000gPrice_Coles)
hist(sugarySnack_data$Per1000gPrice_Coles, xlim = c(-10,100), ylim = c(0, 0.04), col="grey", xlab="Price (per 1000 g or mL)", main="Histogram of Sugary Snacks at Coles (full price)", freq = FALSE)
curve(expr = dnorm(x, mean=mean_Per1000gPrice_Coles, sd = sd_Per1000gPrice_Coles), col="darkblue", lwd=2, add=TRUE)

mean_Per1000gPrice_ColesSale <- mean(sugarySnack_data$Per1000gPrice_ColesSale)
sd_Per1000gPrice_ColesSale <- sd(sugarySnack_data$Per1000gPrice_ColesSale)
hist(sugarySnack_data$Per1000gPrice_ColesSale, xlim = c(-10,100), ylim = c(0, 0.05), col="grey", xlab="Price (per 1000 g or mL)", main="Histogram of Sugary Snacks at Coles (full price)", freq = FALSE)
curve(expr = dnorm(x, mean=mean_Per1000gPrice_Coles, sd = sd_Per1000gPrice_Coles), col="darkblue", lwd=2, add=TRUE)

#Come back to summary stats table
summary(sugarySnack_data$Coles)
summary(sugarySnack_data$'Coles Sale')

s <- ggplot(data=sugarySnack_data, aes(x=Coles))
s + geom_histogram()

s3 <- ggplot(data=ds, aes(x=Coles))
s3 + geom_histogram(aes(fill=ds$`Allocated Category`), colour="Black")

s4 <- ggplot(data=ds, aes(x=Woolworths))
s4 + geom_histogram(aes(fill=ds$`Allocated Category`), colour="Black")




```

```{r pressure, echo=FALSE}
s3 <- ggplot(data=ds, aes(x=Coles))
s3 + geom_histogram(aes(fill=ds$`Allocated Category`), colour="Black")
```


###Say we have 500g for $10, then 1000g would cost $20. To obtain a 1000g normalizing factor, we go (1000(g)/amount(g)), then multiply by price. As above, (1000g/500g)*$10 = $20 per kg 

```{r}
#Creating new data set for allocated category Diet/ Gym Food
#Creating a filter
dietGymFood_filter <- ds$`Allocated Category` == "Diet/ Gym Food"
#Creating the data set
dietGymFood_data <- ds[dietGymFood_filter,]
#Check units
table(dietGymFood_data$`Unit`)
#In this instance we will take grams and mL to be equal (as at SLP, 1 mL has a mass of 1 g)
sugarySnack_data$PriceMass <- 1000 / sugarySnack_data$Amount
sugarySnack_data$Per1000gPrice_Coles <- sugarySnack_data$PriceMass * sugarySnack_data$Coles
#Creating the Coles Sale sugary snack column
sugarySnack_data$Per1000gPrice_ColesSale <- sugarySnack_data$PriceMass * sugarySnack_data$'Coles Sale'
#Stats - Native

mean_sugarySnack_coles <- mean(sugarySnack_data$Coles)
sd_sugarySnack_coles <- sd(sugarySnack_data$Coles)
hist(sugarySnack_data$Coles, xlim = c(0,20), ylim = c(0, 0.35), col="grey", xlab="Price AUD (variable amount g or mL)",main="Histogram of Sugary Snacks at Coles (full price)", breaks = 11, freq = FALSE)
curve(expr = dnorm(x, mean=mean_sugarySnack_coles, sd = sd_sugarySnack_coles), col="darkblue", lwd=2,   add=TRUE)

mean_sugarySnack_colesSale <- mean(sugarySnack_data$'Coles Sale')
sd_sugarySnack_colesSale <- sd(sugarySnack_data$'Coles Sale')
hist(sugarySnack_data$'Coles Sale', xlim = c(0,10), ylim = c(0, 0.5), col="grey", xlab="Price AUD (variable amount g or mL)", main="Histogram of Sugary Snacks at Coles (sale price)", freq = FALSE)
curve(expr = dnorm(x, mean=mean_sugarySnack_colesSale, sd = sd_sugarySnack_colesSale), col="darkblue", lwd=2, add=TRUE)

mean_Per1000gPrice_Coles <- mean(sugarySnack_data$Per1000gPrice_Coles)
sd_Per1000gPrice_Coles <- sd(sugarySnack_data$Per1000gPrice_Coles)
hist(sugarySnack_data$Per1000gPrice_Coles, xlim = c(-10,100), ylim = c(0, 0.04), col="grey", xlab="Price (per 1000 g or mL)", main="Histogram of Sugary Snacks at Coles (full price)", freq = FALSE)
curve(expr = dnorm(x, mean=mean_Per1000gPrice_Coles, sd = sd_Per1000gPrice_Coles), col="darkblue", lwd=2, add=TRUE)

mean_Per1000gPrice_ColesSale <- mean(sugarySnack_data$Per1000gPrice_ColesSale)
sd_Per1000gPrice_ColesSale <- sd(sugarySnack_data$Per1000gPrice_ColesSale)
hist(sugarySnack_data$Per1000gPrice_ColesSale, xlim = c(-10,100), ylim = c(0, 0.05), col="grey", xlab="Price (per 1000 g or mL)", main="Histogram of Sugary Snacks at Coles (full price)", freq = FALSE)
curve(expr = dnorm(x, mean=mean_Per1000gPrice_Coles, sd = sd_Per1000gPrice_Coles), col="darkblue", lwd=2, add=TRUE)

#Come back to summary stats table
summary(sugarySnack_data$Coles)
summary(sugarySnack_data$'Coles Sale') 
```

```{r}

```

```{r}

```


## Hypothesis Test

Use R to perform an appropriate hypothesis test to determine which supermarket is the cheapest. You need to explain your choice of hypothesis test, any assumptions and the significance level. 

```{r}
# This is a chunk for your hypothesis testing code.
```

## Interpretation

Interpret the results of the hypothesis test by interpreting the $p$-value and confidence intervals and commenting on the statistical significance of the findings. 

## Discussion 

Discuss the findings of your investigation. What did you conclude? What were the strengths and limitations of your investigation? What improvements could be made or what would you do differently next time?


